\addcontentsline{toc}{chapter}{Sinopsis / Abstract}

\thispagestyle{plain}
\vspace*{\fill}

\begin{center}
\begin{minipage}{0.86\textwidth}
    \begin{center}
        {\LARGE\bfseries SINOPSIS\par}
    \end{center}
    \vspace{5mm}

    \project\ este o aplicație web destinată evaluării preliminare a anunțurilor pentru autoturisme second-hand. Utilizatorul introduce un link \autovit\ sau \mobilede, iar sistemul extrage caracteristicile vehiculului, normalizează datele și estimează prețul cu ajutorul mai multor modele de regresie. Predicțiile sunt combinate într-o estimare finală ponderată, pe baza căreia este afișat un verdict ușor de interpretat: preț corect, prea mic sau prea mare.

    Lucrarea prezintă colectarea datelor prin web scraping, deduplicarea și pregătirea setului de antrenare, selecția caracteristicilor și compararea algoritmilor SVR, Ridge, KNN, Random Forest, Extra Trees, Gradient Boosting și Voting Regressor. Aplicația include autentificare, istoric individual, toleranță configurabilă, explicații pentru metricile utilizate și recomandări de anunțuri similare. Rezultatele experimentale indică un scor \(R^2\) maxim de aproximativ \(0.923\) și o eroare absolută medie minimă de aproximativ \(2696\) EUR. Principalele limitări sunt dimensiunea și distribuția datasetului, dependența de structura site-urilor externe și lipsa unor informații tehnice complete.
\end{minipage}
\end{center}

\vfill

\begin{center}
\begin{minipage}{0.86\textwidth}
    \begin{center}
        {\LARGE\bfseries ABSTRACT\par}
    \end{center}
    \vspace{5mm}

    \project\ is a web application designed for the preliminary evaluation of second-hand car advertisements. The user submits an \autovit\ or \mobilede\ link, and the system extracts the vehicle characteristics, normalizes the data, and estimates its price using several regression models. Individual predictions are combined into a weighted final estimate, which produces an accessible verdict: fair price, suspiciously low price, or excessive price.

    The thesis presents the complete workflow, including web scraping, deduplication, training-data preparation, feature selection, and the comparison of SVR, Ridge, KNN, Random Forest, Extra Trees, Gradient Boosting, and Voting Regressor models. The application provides authentication, account-specific history, configurable verdict tolerance, explanations of the reported metrics, and recommendations for similar advertisements. Experimental results show a maximum \(R^2\) score of approximately \(0.923\) and a minimum mean absolute error of approximately \(2696\) EUR. The main limitations are the size and distribution of the dataset, dependence on external website structures, and incomplete availability of relevant technical vehicle information.
\end{minipage}
\end{center}

\vspace*{\fill}
\clearpage
